Local Path Planning with Moving Obstacle Avoidance based on Adaptive MPC in ATLASCAR2

### 2019-03-29 Thesis_Latex/Thesis/Chapter2/Chapter2.tex
update thesis

\chapter{Literature Review}
\cite{4651075}
\cite{vsantos2010}
\cite{borelli}
\cite{Skoda:Thesis:2016}

>>>>

\chapter{Literature Review}
In this chapter we introduce the literature survey of the various algorithms used for robot navigation. The navigation methods are divided into two kinds of control: global path planning and local motion control. First we analyze these two types of strategies and then we describe the current situation of Model Prediction which is the control method that we have adopted.
\section{Global Path Searching Method}
Global path planning uses information about a priori model or a map of the enviroment to evaluate the shortest path that allows the motion from a starting point to the goal position.
There are a lot of path planning algorithms, like cell decomposition, road map or potential field, where the calculation of a complete trajectory from a start position to one or more goal positions can be computed off-line. However they produce a reliable path if and only if the map of the enviroment is already available. So, this prior knowledge of the space where the robot can move, must be accessible.
The most famous method developed for global navigation is the Dijkstra algorithm \cite{Dijkstra:1959}. In recent years, an evolution of this method called A* is one of the most used \cite{Hart:1968}: this algorithm gives a complete and optimal global path in static enviroments. However, it was upgraded in D* \cite{Stentz93optimaland} for efficient online searching of a dynamic enviroment, which gives sequences of path points in the known or partially known space. The basic idea of these two methods is the following: minimizing their cost functions, these strategies have the capability of a quickly  redesign when the condistions of the space change, to guarantee an optimal solution of the trajectory from the starting point to the goal location.  
\subsection{The A* Algorithm}
\subsection{The D* Algorithm}
\section{Local Motion Control}
Local Motion Control is related to the real-time motion of the robot inside in unknown enviroment, where monitoring with the sensors, it can detect where are the obstacles and generate a motion to avoid the collision with them.
\subsection{Potential Field Method}
\subsection{Dynamic Window Approach}
\subsection{VFF Approach for Obstacle Avoidance}
\section{MPC in Autonomous Driving}
\cite{4651075}
\cite{vsantos2010}
\cite{borelli}
\cite{Skoda:Thesis:2016}

### 2019-03-29 Thesis_Latex/Thesis/Chapter4/Chapter4.tex
update thesis

In this particular case it is essential to consider the fourth and the fifth restriction in order to allow the ATLASCAR2 to slow down without colliding with the cars in front. The fifth constraint is simply the position of the ATLASCAR2 that updates at each interval, while the fourth constraint, until there is a free lane, is the position of the closest obstacle (both the positions are with respect to the global reference frame). In the calculation of the fourth constraint is necessary  to consider the speed at which the vehicle and the obstacle are moving in order to keep a safe distance.
At the beginning, the vehicle moves with the reference velocity of $v=\SI{20}{m/s}$. When the ATLASCAR2 detects all the other cars on the road, checks if there is a free lane. In the first part of the simulation, the ATLASCAR2 brakes because there is not enough space for overtaking the cars as shown in Fig. \ref{fig:velocity_braking}. A collision would happen if the vehicle continues to follow the initially planned path with the reference velocity. It is possible to notice that the speed decreases because the applied throttle is negative, so a consistent deceleration is set after $\approx\SI{1.5}{s}$ as depicted in Fig. \ref{fig:throttle_braking}. The velocity of the ATLASCAR2 for $\approx\SI{2}{s}$ adapts to that of the closest obstacle. After a few seconds the fastest car moves and makes available the left lane for overtaking. Dramatic changes of steering angle in early stage are observed in Fig. \ref{fig:delta_braking} and consequently also on the heading angle in Fig. \ref{fig:theta_braking}. Then, the ATLASCAR2 returns to the reference velocity during the overtaking of the two obstacles (the applied throttle after $\approx\SI{5}{s}$ is positive). It is seen that the ATLASCAR2 avoids the obstacles and returns to the road center line with a low overshoot.

>>>>

In this particular case it is essential to consider the fourth and the fifth restrictions in order to allow the ATLASCAR2 to slow down without colliding with the cars in front. The fifth constraint is simply the position of the ATLASCAR2 that updates at each interval, while the fourth constraint, until there is a free lane, is the position of the closest obstacle (both the positions are with respect to the global reference frame). In the calculation of the fourth constraint is necessary  to consider the speed at which the vehicle and the obstacle are moving in order to keep a safe distance.
At the beginning, the vehicle moves with the reference velocity of $v=\SI{20}{m/s}$. When the ATLASCAR2 detects all the other cars on the road, checks if there is a free lane. In the first part of the simulation, the ATLASCAR2 brakes because there is not enough space for overtaking the cars as shown in Fig. \ref{fig:velocity_braking}. A collision would happen if the vehicle continues to follow the initially planned path with the reference velocity. It is possible to notice that the speed decreases because the applied throttle is negative, so a consistent deceleration is set after $\approx\SI{1.5}{s}$ as depicted in Fig. \ref{fig:throttle_braking}. The velocity of the ATLASCAR2 for $\approx\SI{2}{s}$ adapts to that of the closest obstacle. After a few seconds the fastest car moves and makes available the left lane for overtaking. Dramatic changes of steering angle in early stage are observed in Fig. \ref{fig:delta_braking} and consequently also on the heading angle in Fig. \ref{fig:theta_braking}. Then, the ATLASCAR2 returns to the reference velocity during the overtaking of the two obstacles (the applied throttle after $\approx\SI{5}{s}$ is positive). It is seen that the ATLASCAR2 avoids the obstacles and returns to the road center line with a low overshoot.

### 2019-03-29 Thesis_Latex/Thesis/Chapter5/Chapter5.tex
update thesis

@@

To describe the elliptic path and to evaluate its curvature, depicted in Figure \ref{fig:curvature_laneFollowing_circular}, the equations are the follows:

@@

	X_\text{ref}&=\displaystyle 15\cos\Big(\frac{V_x\cdot t}{60}\Big)\\
	Y_\text{ref}&=\displaystyle 30\sin\Big(\frac{V_x\cdot t}{60}\Big)  

@@

\begin{figure}[!t]

@@

%LANE FOLLOWING ELLIPTIC - PATH/CURVATURE
\begin{figure}[!h]
	\begin{minipage}[t]{0.5\textwidth}
		\includegraphics[width=\textwidth]{../../MATLAB/lane_following_circular_path/figure/LongitudinalVelocityVsTime_circular.pdf}
		\subcaption{Longitudinal velocity $V_x$ w.r.t. time.}
		\label{fig:longitudinal_velocity_laneFollowing_circular}
	\end{minipage}
	\begin{minipage}[t]{0.5\textwidth}
		\includegraphics[width=\textwidth]{../../MATLAB/lane_following_circular_path/figure/LateralVelocityVsTime_circular.pdf}
		\subcaption{Lateral velocity $V_y$ w.r.t. time.}
		\label{fig:lateral_velocity_laneFollowing_circular}
	\end{minipage}
	\begin{minipage}[t]{0.5\textwidth}
		\includegraphics[width=\textwidth]{../../MATLAB/lane_following_circular_path/figure/AccelerationVsTime_circular.pdf}
		\subcaption{Acceleration $u_1$ w.r.t. time.}
		\label{fig:acceleration_laneFollowing_circular}
	\end{minipage}
	\begin{minipage}[t]{0.5\textwidth}
		\includegraphics[width=\textwidth]{../../MATLAB/lane_following_circular_path/figure/SteeringAngleVsTime_circular.pdf}
		\subcaption{Steering angle $u_2$ w.r.t. time.}
		\label{fig:steering_laneFollowing_circular}
	\end{minipage}
	\begin{minipage}[t]{0.5\textwidth}
		\includegraphics[width=\textwidth]{../../MATLAB/lane_following_circular_path/figure/RelativeYawAngleVsTime_circular.pdf}
		\subcaption{Relative yaw angle $e_2$ w.r.t. time.}
		\label{fig:relative_yaw_angle_laneFollowing_circular}
	\end{minipage}
	\begin{minipage}[t]{0.5\textwidth}
		\includegraphics[width=\textwidth]{../../MATLAB/lane_following_circular_path/figure/LateralDeviationVsTime_circular.pdf}
		\subcaption{Lateral deviation $e_1$ w.r.t. time.}
		\label{fig:lateral_deviation_laneFollowing_circular}
	\end{minipage}
	\caption{Time signals of the ATLASCAR2 in the simulation with an elliptic path.}
	\label{fig:laneFollowing_signals_circular}
\end{figure}

>>>>

	\begin{minipage}[t]{0.49\textwidth}

@@

To describe the elliptic path and to evaluate its curvature, depicted in Figure \ref{fig:curvature_laneFollowing_circular}, the equations are as follows:

@@

	X_\text{ref}&=\displaystyle 15\cos\Bigg(\frac{V_x\cdot t}{60}\Bigg)\\
	Y_\text{ref}&=\displaystyle 30\sin\Bigg(\frac{V_x\cdot t}{60}\Bigg)  

@@

@@

In particular in Figure \ref{fig:laneFollowing_signals_circular} are represented the time signals of the ATLASCAR2 in the simulation with the elliptic path. It is possible to notice that also in this case the vehicle follows the path with a minimal lateral deviation described in the Figure \ref{fig:lateral_deviation_laneFollowing_circular}.

However, the minimum lateral displacement is at the expense of the costant cruise velocity; infact Figure \ref{fig:longitudinal_velocity_laneFollowing_circular} and \ref{fig:lateral_velocity_laneFollowing_circular} show an oscillatory pattern of both longitudinal speed and lateral velocity caused by the continuous change of direction of the road and the length of the latter.

Also in this situation we simulated a small error in the sensor dynamics in order to make the scenario more realistic: we added a 2 percent error to the longitudinal velocity and this is evident from the small noise in the graphs of the steering angle (Figure \ref{fig:steering_laneFollowing_circular}) and the lateral deviation (Figure \ref{fig:lateral_deviation_laneFollowing_circular}).

As previously stated, the vehicle follows the lane and allows us to state that the control system we have designed is efficient and robust.
%LANE FOLLOWING ELLIPTIC - PATH/CURVATURE
\begin{figure}[!h]
	\begin{minipage}[t]{0.5\textwidth}
		\includegraphics[width=\textwidth]{../../MATLAB/lane_following_circular_path/figure/LongitudinalVelocityVsTime_circular.pdf}
		\subcaption{Longitudinal velocity $V_x$ w.r.t. time.}
		\label{fig:longitudinal_velocity_laneFollowing_circular}
	\end{minipage}
	\begin{minipage}[t]{0.5\textwidth}
		\includegraphics[width=\textwidth]{../../MATLAB/lane_following_circular_path/figure/LateralVelocityVsTime_circular.pdf}
		\subcaption{Lateral velocity $V_y$ w.r.t. time.}
		\label{fig:lateral_velocity_laneFollowing_circular}
	\end{minipage}
	\begin{minipage}[t]{0.5\textwidth}
		\includegraphics[width=\textwidth]{../../MATLAB/lane_following_circular_path/figure/AccelerationVsTime_circular.pdf}
		\subcaption{Acceleration $u_1$ w.r.t. time.}
		\label{fig:acceleration_laneFollowing_circular}
	\end{minipage}
	\begin{minipage}[t]{0.5\textwidth}
		\includegraphics[width=\textwidth]{../../MATLAB/lane_following_circular_path/figure/SteeringAngleVsTime_circular.pdf}
		\subcaption{Steering angle $u_2$ w.r.t. time.}
		\label{fig:steering_laneFollowing_circular}
	\end{minipage}
	\begin{minipage}[t]{0.5\textwidth}
		\includegraphics[width=\textwidth]{../../MATLAB/lane_following_circular_path/figure/RelativeYawAngleVsTime_circular.pdf}
		\subcaption{Relative yaw angle $e_2$ w.r.t. time.}
		\label{fig:relative_yaw_angle_laneFollowing_circular}
	\end{minipage}
	\begin{minipage}[t]{0.5\textwidth}
		\includegraphics[width=\textwidth]{../../MATLAB/lane_following_circular_path/figure/LateralDeviationVsTime_circular.pdf}
		\subcaption{Lateral deviation $e_1$ w.r.t. time.}
		\label{fig:lateral_deviation_laneFollowing_circular}
	\end{minipage}
	\caption{Time signals of the ATLASCAR2 in the simulation with an elliptic path.}
	\label{fig:laneFollowing_signals_circular}
\end{figure}

### 2019-03-29 Thesis_Latex/Thesis/Introduction/Introduction.tex
update thesis

Chapter 2

>>>>

Chapter 2 focuses on some of the more theoretical aspects of this dissertation with a brief introduction to path planning, a literature review related to local navigation algorithms with a special section centred on MPC control strategy for obstacle avoidance and tracking.

In Chapter 3, the theory of Model Predictive Control is discussed in detail to highlight working principle and its characteristics (tuning parameters, stability and robustness). In particular for this work we used an advanced control strategy based on this paradigm called Adaptive MPC that uses a fixed model structure, but allows the model parameters to evolve with the time.

Chapter 4 is used to present the Obstacle Avoidance method that we have developted. First we introduced the case-study model, then we designed the decision making alghorithm and the controller. Finally we verified the control strategy in different scenarios.

Chapter 5 focuses on the Lane Following alghoritm based on Adaptive Model Predictive Control. We considered a different model in which we have applied the bicycle model of lateral vehicle dynamics and approximated the longitudinal dynamics using a first order transfer function.
Then we developed the overall control scheme considering different paths to follow.

### 2019-03-29 Thesis_Presentation/Presentazione/Presentation.tex
update thesis

\documentclass{beamer}

\usetheme{Padova}

\title{Local Path Planning with Moving Obstacle Avoidance based on Adaptive MPC in ATLASCAR2}
\author{Alberto Franco 1156523}
\date{15 Aprile 2019}

@@

	\begin{frame}{First section}
		\begin{block}{Normal block}
			Fusce luctus venenatis felis quis semper
		\end{block}

		\begin{alertblock}{Alert block}
			$$ E = (x_1 \vee \neg x_2 \vee \neg x_3) \wedge (x_1 \vee x_2 \vee x_4) $$
		\end{alertblock}

		\begin{exampleblock}{Example block}
			Proin tincidunt, neque at tincidunt mollis
		\end{exampleblock}
	\end{frame}

>>>>

\documentclass{beamer}
\usetheme{Padova}
\usepackage{movie15}
\usepackage{media9}
\title{Local Path Planning with Moving Obstacle Avoidance based on Adaptive MPC in ATLASCAR2}
\subtitle{\itshape Tesi di Laurea in Ingegneria dell'Automazione}
\author{Relatore: Prof. Angelo Cenedese\qquad\quad Laureando: Alberto Franco Correlatore: Prof. Vitor Santos}
\date{\vspace{0.4cm}15 Aprile 2019}

@@

	\begin{frame}{First section}
		\includemedia[
		label=myVidPlayer,
		width=6cm,height=6cm,
		activate=pageopen,
		addresource=./videos/animation_6_obstacles.avi,
		flashvars={
			source=./videos/animation_6_obstacles.avi %video to be shown at first
			&autoPlay=true
			&scaleMode=letterbox %useful, if videos are of different aspect ratio
		}
		]{}{VPlayer.swf}

		\mediabutton[mediacommand=myVidPlayer:setSource [(./videos/animation_6_obstacles.avi)]]{animation.avi}
	\end{frame}
